\tw: a Xanalogical Storage and Authoring System

### 2003-02-15 papers/hypertext2003/paper.tex
Finished changes in response to Jim's comments.

Much of the existing work on xanalogical systems was discussed in Sections \ref{sec:Introduction} and \ref{sec:Xanadu}, so we will focus on related non-xanalogical systems here.
However, we should mention that interest in Xanadu has not waned in recent years.
For example, Lukka and Fallenstein describe a system that uses ideas taken from Freenet for xanalogical content storage and retrieval \cite{FreenetXanadu}.
Recent work with XLink has focused on adding transclusion capabilities to the web \cite{Lowe2001}, but support is limited to embedding entire documents.
XPointer can be used in conjunction with XLink to refer to document spans \cite{Vitali2002}, though nothing prevents these references from breaking when documents change.

@@

\section{Conclusion}
Thoughout this paper, we have discussed the strategies that made \tw \  development possible, including an interative process and heavy use of existing technology.

>>>>

Much of the existing work on xanalogical systems was discussed in Sections \ref{sec:Introduction} and \ref{sec:Xanadu}, so we will focus on related non-xanalogical systems here.

However, we should mention that interest in Xanadu has not waned in recent years, even though development work on Udanax, the last official (and most ambitious) Xanadu implementation effort, ceased in 1995 \cite{Udanax}.
For example, Lukka and Fallenstein describe a system that uses ideas taken from Freenet for xanalogical content storage and retrieval \cite{FreenetXanadu}.
As another example, recent work with XLink has focused on adding transclusion capabilities to the web \cite{Lowe2001}, but support is limited to embedding entire documents.
XPointer can be used in conjunction with XLink to refer to document spans \cite{Vitali2002}, though nothing prevents these references from breaking when documents change.

@@

\section{Conclusion}
Thoughout this paper, we have discussed the strategies that made \tw \  development possible, including an iterative process and heavy use of existing technology.
